Bioverse: Origins of Life

### 2024-07-10 src/tex/ms.tex
describe transit survey, measurements, precision

\subsubsection{Transit survey (e.g., Nautilus)}

@@

... measure the maximum past \gls{NUV} flux with a precision of \var{nautilus_max_nuv} and the instellation that a planet receives with a precision of \var{nautilus_S}.

>>>>

\subsubsection{Transit survey simulations}
With the synthetic star and planet samples generated, we simulated observations of these planets with a hypothetical transit survey.
Using Bioverse's survey module, we simulated noisy measurements of key observables assuming a capable transit survey that can characterize a large sample with high photometric precision.
We roughly followed the mission parameters of the Nautilus mission concept~\citep{Apai2019,Apai2022} and measured planetary instellation (for \gls{HZ} occupancy) with a precision of \var{nautilus_S} and host star effective temperature with a precision of \var{nautilus_T_eff_st}~K.
We assumed that the maximum past \gls{NUV} flux a planet received can be determined within a precision of \var{nautilus_max_nuv}.
To marginalize over choices of biosignatures and their detectability, which are beyond the scope of this study, we assumed that any inhabited planet would show a biosignature detectable by the survey.

@@
